Understanding and Verifying the Shape of Stencil Computations

### 2017-03-25 oopsla17/lattice-model.tex
Complete equational theory proof

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{fixltx2e}

@@

\theoremstyle{plain}
\newtheorem{lem}{Lemma}
\newtheorem{prop}{Proposition}

@@

\newcommand{\zinf}{\textnormal{$\mathbb{Z}_\infty$}}
\newcommand{\interp}[1]{\llbracket\texttt{#1}\rrbracket}
\newcommand{\interv}[3]{\textnormal{$\lbrack#1,#2\rbrack^{#3}$}}
\newcommand{\vecgen}[3]{\textnormal{$\textit{vec-gen}_{#1}(#2,#3)$}}
\newcommand{\textcap}[1]{\texttt{\textit{#1}}}

@@

\begin{prop}{}
  We have the following identity for \zinf{} intervals:
%
  \begin{equation*}
    \interv{a}{b}{c} \cap \interv{d}{e}{f} =
      \interv{\max \{a,d\}}{\min \{b,e\}}{\neg c \vee \neg f}
  \end{equation*}\label{def:zinf-intersect}
\end{prop}
%
\begin{proof}
  \begin{align*}
    \interv{a}{b}{c} \cap \interv{d}{e}{f} = &
      \; \{ n \;|\; a \leq n \leq b \wedge (\neg c \implies n \neq 0) \}
      \;\cap \\
      & \; \{ n \;|\; d \leq n \leq e \wedge (\neg f \implies n \neq 0) \}
      \\
    = & \; \{ n \;|\; \max \{a,d\} \leq n \leq \min \{b,e\} \wedge (\neg c
      \vee \neg f \implies n \neq 0) \} \\
    = & \; \interv{\max{\{a,d\}}}{\min{\{b,e\}}}{\neg c \vee \neg f}
  \end{align*}
\end{proof}

%\begin{prop}{}
%  $(\textit{Interval}, \supseteq)$ is a sublattice of
%  $(\mathcal{P}(\zinf{}),\supseteq)$ with \interv{-\infty}{\infty}{\textsf{p}}
%  and \interv{0}{0}{\textsf{np}} as its top and bottom elements.
%\end{prop}
%%
%\begin{proof}
%  We know $\textit{Interval} \subseteq \mathcal{P}(\zinf{})$ since intervals
%  represents sets drawn from {\zinf{}}
%
%  Let \interv{a}{b}{c} and \interv{d}{e}{f} be two arbitrary \zinf{} intervals.
%  We need to show that their meet and join both lie in \textit{Interval}.
%%
%  \begin{align*}
%    \interv{a}{b}{c} \wedge \interv{d}{e}{f} = &
%      \{ n \;|\; a \leq n \leq b \wedge (c = \textsf{np} \implies n \neq 0) \}
%      \;\cup \\
%      & \{ n \;|\; d \leq n \leq e \wedge (f = \textsf{np} \implies n \neq 0) \}
%      \\
%    = & \{ n \;|\; \min{a,d} \leq n \leq \max{b,e} \wedge ((c =
%      \textsf{np} \wedge f = \textsf{np}) \implies n \neq 0) \} \\
%    = & \interv{\min{\{a,d\}}}{\max{\{b,e\}}}{k}
%  \end{align*}
%%
%  where $k$ is \textsf{np} if both $c$ and $d$ are \textsf{np} and \textsf{p}
%  otherwise. Minimum of lower bound is still negative or zero and maximum of
%  upper bounds is still positive or zero, hence the meet lies in
%  \textit{Interval}.
%%
%  \begin{align*}
%    \interv{a}{b}{c} \vee \interv{d}{e}{f} = &
%      \{ n \;|\; a \leq n \leq b \wedge (c = \textsf{np} \implies n \neq 0) \}
%      \;\cap \\
%      & \{ n \;|\; d \leq n \leq e \wedge (f = \textsf{np} \implies n \neq 0) \}
%      \\
%    = & \{ n \;|\; \max{a,d} \leq n \leq \min{b,e} \wedge ((c =
%      \textsf{np} \vee f = \textsf{np}) \implies n \neq 0) \} \\
%    = & \interv{\max{\{a,d\}}}{\min{\{b,e\}}}{k}
%  \end{align*}
%%
%  where $k$ is \textsf{np} if either $c$ or $d$ are \textsf{np} and \textsf{p}
%  otherwise. Maximum of lower bound is still negative or zero and minimum of
%  upper bounds is still positive or zero, hence the join lies in
%  \textit{Interval}.
%
%  \interv{-\infty}{\infty}{\textsf{p}} is then \zinf{} and
%  \interv{0}{0}{\textsf{np}} is $\emptyset$. Since these are in the sublattice
%  and they are the bottom and top elements in the parent lattice, they are
%  necessarily the bottom and top elements in the sublattice.
%\end{proof}

%\begin{prop}{}
%  $(\textit{Interval},\supseteq)$ is a distributive lattice.
%\end{prop}
%%
%\begin{proof}
%  It is enough to show for arbitrary $\interv{a}{b}{c}$, $\interv{d}{e}{f}$,
%  $\interv{g}{h}{i}$ in \textit{Interval}, $\interv{a}{b}{c} \vee
%  (\interv{d}{e}{f} \wedge \interv{g}{h}{i}) = (\interv{a}{b}{c} \vee
%  \interv{d}{e}{f}) \wedge (\interv{a}{b}{c} \vee \interv{g}{h}{i})$. When this
%  holds the dual law also holds. The property immediately follows from
%  definition due to distributivity of set intersection over union.
%\end{proof}

@@

@@

  The set of $N$ dimensional vector intervals is $\textit{Interval}^N$.
\end{defn}

\begin{lem}{}
  Intersection distributes over vector intervals.
%
  \begin{equation*}
    (\textit{vint}_1, \dots, \textit{vint}_N) \;\cap\;
      (\textit{vint'}_1, \dots, \textit{vint'}_N)
      =
    (\textit{vint}_1 \;\cap\; \textit{vint'}_1, \dots,
     \textit{vint}_N \;\cap\; \textit{vint'}_N)
  \end{equation*}\label{lem:vector-dist}
\end{lem}
%
\begin{prop}{}
  We have the following identity for $N$ dimensional vector intervals:
%
  \begin{gather*}
    (\interv{a_1}{b_1}{c_1}, \dots, \interv{a_N}{b_N}{c_N}) \; \cap \;
      (\interv{a'_1}{b'_1}{c'_1}, \dots, \interv{a'_N}{b'_N}{c'_N}) \\
    = \\
    (\interv{\max \{a_1,a'_1\}}{\min \{b_1,b'_1\}}{\neg c_1 \vee \neg c'_1},
      \dots, \interv{\max \{a_N,a'_N\}}{\min \{b_N,b'_N\}}{\neg c_N \vee \neg c'_N})
  \end{gather*}
\end{prop}
%
\begin{proof}
  This immediately follows from \Cref{lem:vector-dist} and
  \Cref{def:zinf-intersect}.
\end{proof}

@@

We give some basic interpretations: $\interp{\texttt{n}} = n$ where $n$ is in
$\mathbb{Z}$, $\interp{pointed} = \llbracket \epsilon \rrbracket =
\textsf{true}$, $\interp{\texttt{nonpointed}} = \textsf{false}$.
Typographically, cursive font is used within specifications to indicate a
partial textual capture.

@@

First, we give meaning to region constants (introduced in \Cref{}).
%
\begin{align*}
  \interp{\texttt{pointed(dim=\textit{i})}}_N & =
    \vecgen{N}{\interp{\textit{i}}}{\interv{0}{0}{\textsf{true}}}\\
%
  \interp{\texttt{centered(dim=\textit{i}, depth=\textit{k}, \textit{p})}}_N & =
    \vecgen{N}
           {\interp{\textit{i}}}
           {\interv{-\interp{\textit{k}}}
                   {\interp{\textit{k}}}
                   {\interp{\textit{p}}}
           } \\
%
  \interp{\texttt{forward(dim=\textit{i}, depth=\textit{k}, \textit{p})}}_N & =
    \vecgen{N}
           {\interp{\textit{i}}}
           {\interv{0}
                   {\interp{\textit{k}}}
                   {\interp{\textit{p}}}
           } \\
%
  \interp{\texttt{backward(dim=\textit{i}, depth=\textit{k}, \textit{p})}}_N & =
    \vecgen{N}
           {\interp{\textit{i}}}
           {\interv{-\interp{\textit{k}}}
                   {0}
                   {\interp{\textit{p}}}
           }
\end{align*}

Second, we provide the semantics for the permissive region operator, \texttt{+},
and the restrictive region operator, \texttt{*}, by associating them with meet
and join respectively. Let \texttt{\textit{R}} and \texttt{\textit{S}} be
regions.
%
\begin{align*}
  \interp{\texttt{\textit{R} + \textit{S}}}_N & =
    \interp{\texttt{\textit{R}}}_N \wedge \interp{\texttt{\textit{S}}}_N
&
  \interp{\texttt{\textit{R} * \textit{S}}}_N & =
    \interp{\texttt{\textit{R}}}_N \vee \interp{\texttt{\textit{S}}}_N
\end{align*}

Third, we need to mark presence of modifiers such as \texttt{readOnce} and
\texttt{atMost} as introduced in \Cref{}. In the context of
multiplicity modifiers we have the following semantics:
%
\begin{align*}
  \interp{readOnce} & = \textsf{mult} &
  \llbracket\epsilon\rrbracket & = \textsf{once}
\end{align*}

In the context of approximation modifiers, we have
%
\begin{align*}
  \interp{atLeast} & = \textsf{lower} &
  \interp{atMost} & = \textsf{upper} &
  \llbracket \epsilon \rrbracket = \textsf{exact}
\end{align*}

Finally, we can give full semantics of a stencil specification:
%
\begin{equation*}
  \interp{stencil \textit{Mult}, \textit{Appr}, \textit{Region}} =
    \interp{\textit{Mult}}{(\interp{\textit{Appr}}(\interp{\textit{Region}}))}
\end{equation*}

@@

We know introduce the equational and approximation theory of stencil
specifications based on $\equiv$ and $<\:$.

@@

\begin{description}
  \item[Basic] \texttt{*} and \texttt{+} are both idempotent, commutative, and
    associative;
%
  \item[Dist] \texttt{*} distributed over \texttt{+} and dually
    \texttt{+} distributes over \texttt{*}, meaning if \textcap{R}, \textcap{S},
    and \textcap{T} are regions, then we have the following equivalences:
%
    \begin{align*}
      \texttt{\textcap{R}*(\textcap{S}+\textcap{T})} & \equiv
        \texttt{(\textcap{R}*\textcap{S})+(\textcap{R}*\textcap{T})} &
      \texttt{\textcap{R}+(\textcap{S}*\textcap{T})} & \equiv
        \texttt{(\textcap{R}+\textcap{S})*(\textcap{R}+\textcap{T})}
    \end{align*}
%
  \item[Overlapping pointed] If \textcap{R} is one of \texttt{forward},
    \texttt{backward}, or \texttt{centered}, then we have
    $\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n},\_) +
    pointed(dim=\textcap{n})} \equiv
    \texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n})}$.
%
  \item[Centered] The region constants \texttt{forward} and \texttt{backward}
    are two halves of \texttt{centered} specifications:
%
    \begin{gather*}
      \texttt{centered(depth=\textcap{k},dim=\textit{n},\textcap{p1})} \\
      \equiv \\
      \texttt{forward(depth=\textcap{k},dim=\textit{n},\textcap{p2}) +
        backward(depth=\textcap{k},dim=\textit{n},\textcap{p3})}
    \end{gather*}
%
    Here \textcap{p1} is \texttt{nonpointed} if both \textcap{p1} and
    \textcap{p3} are \texttt{nonpointed} and \texttt{pointed} otherwise.
\end{description}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{indentfirst}
\usepackage{cleveref}

@@

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{case}{Case}

@@

\newcommand{\zinf}{\textnormal{$\mathbb{Z}_\infty$}}
\newcommand{\interp}[1]{\llbracket#1\rrbracket}
\newcommand{\interv}[3]{\textnormal{$\lbrack#1,#2\rbrack^{#3}$}}
\newcommand{\vecgen}[3]{\textnormal{$\textit{vec-gen}_{#1}(#2,#3)$}}
\newcommand{\textcap}[1]{\texttt{\textit{#1}}}

@@

\begin{lem}{}
  We have the following dual identities for \zinf{} intervals:
%
  \begin{align*}
    \interv{a}{b}{c} \cap \interv{d}{e}{f} & =
      \interv{\max \{a,d\}}{\min \{b,e\}}{c \wedge f} \\
    \interv{a}{b}{c} \cup \interv{d}{e}{f} & =
      \interv{\min \{a,d\}}{\max \{b,e\}}{c \vee f}
  \end{align*}\label{lem:zinf-identities}
\end{lem}
%
\begin{proof}
  We give the proof of the first identity and the second one is similar.
  \begin{align*}
    \interv{a}{b}{c} \cap \interv{d}{e}{f} = &
      \; \{ n \;|\; a \leq n \leq b \wedge (\neg c \implies n \neq 0) \}
      \;\cap \\
      & \; \{ n \;|\; d \leq n \leq e \wedge (\neg f \implies n \neq 0) \}
      \\
    = & \; \{ n \;|\; \max \{a,d\} \leq n \leq \min \{b,e\} \wedge (\neg c
      \vee \neg f \implies n \neq 0) \} \\
    = & \; \interv{\max{\{a,d\}}}{\min{\{b,e\}}}{\neg c \vee \neg f}
  \end{align*}
\end{proof}

@@

\begin{lem}{}
  Intersection distributes over offsets vectors.
%
  \begin{equation*}
    (\textit{vint}_1, \dots, \textit{vint}_N) \;\cap\;
      (\textit{vint'}_1, \dots, \textit{vint'}_N)
      =
    (\textit{vint}_1 \;\cap\; \textit{vint'}_1, \dots,
     \textit{vint}_N \;\cap\; \textit{vint'}_N)
  \end{equation*}\label{lem:vector-intersect}
\end{lem}

\begin{lem}{}
  Let $v$ and $v'$ be two $N$ dimensional offsets vectors such that $v_i$ is
  equal to $v'_i$ for all $1 \leq i \leq N$ except $k$, then we have the
  following:
%
  \begin{equation*}
    (v_1,\dotsc, v_k,\dotsc, v_N) \; \cup \; (v'_1,\dotsc, v'_k, \dotsc, v_N)
    =
    (v_1,\dotsc, v_k \cup v'_k,\dotsc, v_N)
  \end{equation*}\label{lem:vector-union}
\end{lem}
%
\begin{proof}
  \begin{align*}
    v \; \cup \; v' &
    = \{(x_1,\dotsc,x_n) \mid
          \bigwedge_{1 \leq i \leq N } x_i \in v_i \}
      \;\cup\;
      \{(x_1,\dotsc,x_n) \mid
          \bigwedge_{1 \leq i \leq N } x_i \in v'_i \} \\
    & = \{(x_1,\dotsc,x_n) \mid
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v_i
              \wedge x_k \in v_k \vee
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v'_i
            \wedge x_k \in v'_k
        \} \\
    & = \{(x_1,\dotsc,x_n) \mid
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v_i
          \wedge x_k \in v_k \cup v'_k
        \} \\
    & = (v_1,\dotsc, v_k \cup v'_k,\dotsc, v_N)
  \end{align*}
\end{proof}

@@

  The set of $N$ dimensional vector intervals is $\textit{Interval}^N$. Every
  vector interval is also an offsets vector.
\end{defn}

\begin{lem}{}
  Intersection distributes $N$ dimensional vector intervals:
%
  \begin{gather*}
    (\interv{a_1}{b_1}{c_1}, \dots, \interv{a_N}{b_N}{c_N}) \; \cap \;
      (\interv{a'_1}{b'_1}{c'_1}, \dots, \interv{a'_N}{b'_N}{c'_N}) \\
    = \\
    (\interv{\max \{a_1,a'_1\}}{\min \{b_1,b'_1\}}{\neg c_1 \vee \neg c'_1},
      \dots, \interv{\max \{a_N,a'_N\}}{\min \{b_N,b'_N\}}{\neg c_N \vee \neg c'_N})
  \end{gather*}
\end{lem}
%
\begin{proof}
  This immediately follows from \Cref{lem:vector-intersect} and
  \Cref{lem:zinf-identities}.
\end{proof}

@@

We give some basic interpretations: $\interp{\texttt{n}} = n$ where $n$ is in
$\mathbb{Z}$, $\interp{\texttt{pointed}} = \llbracket \epsilon \rrbracket =
\textsf{true}$, $\interp{\texttt{nonpointed}} = \textsf{false}$.
Typographically, cursive font is used within specifications to indicate a
partial textual capture.

@@

First, we give meaning to region constants (introduced in \Cref{}).
%
\begin{align*}
  \interp{\texttt{pointed(dim=\textcap{i})}}_N & =
    \vecgen{N}{\interp{\textcap{i}}}{\interv{0}{0}{\textsf{true}}}\\
%
  \interp{\texttt{centered(dim=\textcap{i}, depth=\textcap{k}, \textcap{p})}}_N
    & = \vecgen{N}
           {\interp{\textcap{i}}}
           {\interv{-\interp{\textcap{k}}}
                   {\interp{\textcap{k}}}
                   {\interp{\textcap{p}}}
           } \\
%
  \interp{\texttt{forward(dim=\textcap{i}, depth=\textcap{k}, \textcap{p})}}_N
    & = \vecgen{N}
           {\interp{\textcap{i}}}
           {\interv{0}
                   {\interp{\textcap{k}}}
                   {\interp{\textcap{p}}}
           } \\
%
  \interp{\texttt{backward(dim=\textcap{i}, depth=\textcap{k}, \textcap{p})}}_N
    & = \vecgen{N}
           {\interp{\textcap{i}}}
           {\interv{-\interp{\textcap{k}}}
                   {0}
                   {\interp{\textcap{p}}}
           }
\end{align*}

Second, we provide the semantics for the permissive region operator, \texttt{+},
and the restrictive region operator, \texttt{*}, by associating them with meet
and join respectively. Let \texttt{\textit{R}} and \texttt{\textit{S}} be
regions.
%
\begin{align*}
  \interp{\texttt{\textcap{R} + \textcap{S}}}_N & =
    \interp{\textcap{R}}_N \wedge \interp{\textcap{S}}_N
&
  \interp{\texttt{\textcap{R} * \textcap{S}}}_N & =
    \interp{\textcap{R}}_N \vee \interp{\textcap{S}}_N
\end{align*}

Third, we need to mark presence of modifiers such as \texttt{readOnce} and
\texttt{atMost} as introduced in \Cref{}. In the context of
multiplicity modifiers we have the following semantics:
%
\begin{align*}
  \interp{\texttt{readOnce}} & = \textsf{mult} &
  \llbracket\epsilon\rrbracket & = \textsf{once}
\end{align*}

In the context of approximation modifiers, we have
%
\begin{align*}
  \interp{\texttt{atLeast}} & = \textsf{lower} &
  \interp{\texttt{atMost}} & = \textsf{upper} &
  \llbracket \epsilon \rrbracket = \textsf{exact}
\end{align*}

Finally, we can give full semantics of a stencil specification:
%
\begin{equation*}
  \interp{\texttt{stencil \textcap{Mult}, \textcap{Appr}, \textcap{Region}}} =
    \interp{\textcap{Mult}}
           {(\interp{\textcap{Appr}}
                    {(\interp{\textcap{Region}})})}
\end{equation*}

@@

We know introduce the equational and approximation theory of stencil
specifications based on $\equiv$ and $\prec$.

@@

\begin{description}
  \item[Basic] \texttt{*} and \texttt{+} are both idempotent, commutative, and
    associative;
%
  \item[Dist] \texttt{*} distributed over \texttt{+} and dually
    \texttt{+} distributes over \texttt{*}, meaning if \textcap{R}, \textcap{S},
    and \textcap{T} are regions, then we have the following equivalences:
%
    \begin{align*}
      \texttt{\textcap{R}*(\textcap{S}+\textcap{T})} & \equiv
        \texttt{(\textcap{R}*\textcap{S})+(\textcap{R}*\textcap{T})} &
      \texttt{\textcap{R}+(\textcap{S}*\textcap{T})} & \equiv
        \texttt{(\textcap{R}+\textcap{S})*(\textcap{R}+\textcap{T})}
    \end{align*}
%
  \item[Overlapping pointed] If \textcap{R} is one of \texttt{forward},
    \texttt{backward}, or \texttt{centered}, then we have
    $\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n},\_) +
    pointed(dim=\textcap{n})} \equiv
    \texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n})}$.
%
  \item[Centered] The region constants \texttt{forward} and \texttt{backward}
    are two halves of \texttt{centered} specifications:
%
    \begin{gather*}
      \texttt{centered(depth=\textcap{k},dim=\textit{n},\textcap{p1})} \\
      \equiv \\
      \texttt{forward(depth=\textcap{k},dim=\textit{n},\textcap{p2}) +
        backward(depth=\textcap{k},dim=\textit{n},\textcap{p3})}
    \end{gather*}
%
    Here \textcap{p1} is \texttt{nonpointed} if both \textcap{p2} and
    \textcap{p3} are \texttt{nonpointed} and \texttt{pointed} otherwise.
%
  \item[Point] Let \textcap{R} and \textcap{S} be region constants with two
    variants a superscript \textit{f} to mean nonpointed and \textit{t} to mean
    pointed and \textcap{dr} \& \textcap{ds} be the dimensions \textcap{R} and
    \textcap{S} acts on. Then we have the following dual equivalences:
%
    \begin{align*}
      (\textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{f}})
      \;\texttt{+}\;
      (\textcap{R}^{\textit{f}} \texttt{*} \textcap{S}^{\textit{t}})
      \;\texttt{+}\;
      \texttt{p(dim=\textcap{dr})*p(dim=\textcap{ds})} & =
        \textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}} \\
%
      (\textcap{R}^{\textit{t}} \texttt{+} \textcap{S}^{\textit{f}}) \texttt{*}
      (\textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{t}}) & =
        \textcap{R}^{\textit{f}} \texttt{+} \textcap{S}^{\textit{f}}
        \;\texttt{+}\;
        \texttt{p(dim=\textcap{dr})*p(dim=\textcap{ds})}
    \end{align*}
\end{description}

\begin{thm}{(Soundness)}
  Equational theory is sound with respect to the lattice model. Let $R$
  and $S$ be $N$ dimensional regions, then we have
%
  \begin{equation*}
    R \equiv S \implies \interp{R}_N \equiv \interp{S}_N
  \end{equation*}
\end{thm}

\begin{proof}
  We show soundness for each of the equivalences.
  \begin{description}
    \item[Basic] These follow from basic properties of lattices.
%
    \item[Dist] This is immediate from the definition of distributive
      lattice which the model is one.
%
    \item[Overlapping pointed] Let $\interp{\textcap{n}}$ be $n$. Counterparts
      of individual regions for some Boolean $p$ are given below:
%
      \begin{align*}
        \interp{\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n},\_)}}_N
        & = \vecgen{N}{n}{\interv{-k}{k}{p}} \\
%
        \interp{\texttt{pointed(dim=\textcap{n})}}_N
        &= \vecgen{N}{n}{\interv{0}{0}{\textsf{true}}} \\
%
        \interp{\texttt{\textcap{R}(depth=\textcap{k},dim=\textcap{n})}}_N
        &= \vecgen{N}{n}{\interv{-k}{k}{\textsf{true}}}
      \end{align*}

      Using \Cref{lem:vector-union}, it is sufficient to show
      $ \interv{-k}{k}{p} \;\cup\; \interv{0}{0}{\textsf{true}} =
        \interv{-k}{k}{\textsf{true}} $ holds. This immediately follows from
      \Cref{lem:zinf-identities}.
%
    \item[Centered] Let $\interp{\textcap{n}}$, $\interp{\textcap{k}}$,
      $\interp{\textcap{p1}}$, $\interp{\textcap{p2}}$, and
      $\interp{\textcap{p3}}$ be $n$, $k$, $p1$, $p2$, and $p3$ respectively. We
      also know that $p1$ is $p2 \vee p3$ from \textbf{Centered} detinition.
      Then we get the following interpretation for region constants involved in
      the equivalence:
%
      \begin{align*}
        \interp{\texttt{centered(depth=\textcap{k},dim=\textit{n},\textcap{p1})}}_N
          &= \vecgen{N}{n}{\interv{-k}{k}{p2 \vee p3}} \\
%
        \interp{\texttt{forward(depth=\textcap{k},dim=\textit{n},\textcap{p2})}}_N
          &= \vecgen{N}{n}{\interv{0}{k}{p2} }\\
%
        \interp{\texttt{backward(depth=\textcap{k},dim=\textit{n},\textcap{p3})}}_N
          &= \vecgen{N}{n}{\interv{0}{k}{p3}}
      \end{align*}
%
      Using \Cref{lem:vector-union}, it is sufficient to show $\interv{-k}{k}{p2
      \vee p3} = \interv{0}{k}{p2} \cup \interv{-k}{0}{p3}$ holds. This
      immediately follows from \Cref{lem:zinf-identities}.

    \item[Point] Let $\interp{\textcap{R}^{\textnormal{\textit{p}}}}_N$ and
      $\interp{\textcap{S}^{\textnormal{\textit{p'}}}}_N$ be
      $\vecgen{N}{k}{\interv{a}{b}{p}}$ and $\vecgen{N}{l}{\interv{c}{d}{p'}}$
      respectively for some $a$ and $c$ less than or equal to 0, for some $c$
      and $d$ greater than or equal to 0, for some indices $k$ and $l$ be
      $\interp{\textcap{dr}}$ and $\interp{\textcap{ds}}$, which are not
      necessarily distinct and $p$ and $p'$ are \textsf{true} if pointed and
      \textsf{false} otherwise.
%
      \begin{align*}
        \hspace{2em&\hspace{-2em}}
        \interp
          {{(\textcap{R}^{\textit{t}} * \textcap{S}^{\textit{f}})}
           \;\texttt{+}\;
           {(\textcap{R}^{\textit{f}} * \textcap{S}^{\textit{t}})}
           \;\texttt{+}\;
           \texttt{pointed(dim=\textcap{dr})*pointed(dim=\textcap{ds})}}_N \\
        & = {(\interp{\textcap{R}^{\textit{t}}}_N \cap
              \interp{\textcap{S}^{\textit{f}}}_N)} \cup
            {(\interp{\textcap{R}^{\textit{f}}}_N \cap
              \interp{\textcap{S}^{\textit{t}}}_N)} \;\cup \\
        & \quad\,\, {(\vecgen{N}{\interp{ds}}{\interv{0}{0}{\textsf{true}}}
                      \;\cup\;
                      \vecgen{N}{\interp{dr}}{\interv{0}{0}{\textsf{true}}})} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge {(c \leq x_l \leq d \wedge x_l \neq 0)} \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge {(a \leq x_k \leq b \wedge x_k \neq 0)}
            \wedge c \leq x_l \leq d \} \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
          \wedge c \leq x_l \leq d \wedge {(x_k \neq 0 \vee x_l \neq 0)} \}
          \;\cup \\
        & \quad\,\, \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge (x_k = 0 \wedge x_l = 0) \} \\
        & = \{ x \mid
            \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k \neq l}} x_i \in
              \interv{\infty}{\infty}{\textsf{true}}
            \wedge a \leq x_k \leq b
            \wedge c \leq x_l \leq d \} \\
        & = \textcap{R}^{\textit{t}} \texttt{*} \textcap{S}^{\textit{t}}
      \end{align*}
  \end{description}
\end{proof}
